---
title: "Sensitivity Analysis of Atmospheric Conductance"
author: "Alessandra Vidal Meza, Kiran Favre"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
# Load libraries
library(tidyverse)
library(lhs)
library(sensitivity)
library(purrr)

# Import function
source("src/catm.R")

# Set seed to randomize
set.seed(7)
```

## Objective

For a given forest, you will perform a sensitivity analysis of model
predictions of conductance. Atmospheric conductance refers to how easily
vapor diffuses from vegetation surfaces.

Consider the sensitivity of your estimate to uncertainty in the
following parameters and inputs: - $h$ is vegetation height (cm) - $k_d$
is a parameter; default 0.7 - $k_0$ is a parameter; default 0.1 - $v$ is
windspeed (cm/s)

### Assumptions

-   Assume windspeed, $v$, is normally distributed with a mean of 250
    cm/s; a standard deviation of 30 cm/s
-   Assume vegetation height, $h$, is somewhere between 9.5 and 10.5 m
    (but any value in that range is equally likely)
-   Assume the $k_d$ and $k_0$ are normally distributed; standard
    deviation of 1% of their default values

## Latin Hypercube Sampling

Let's use the Latin hypercube approach to generate parameter values for
the parameters and inputs:

```{r}
# Define parameters and inputs
par_names <- c("v", "height", "k_o", "k_d")

# Extract number of parameters and inputs
n_par <- length(par_names)

# Set number of samples
n_sample <- 100

# Create a matrix with random samples
par_quant <- randomLHS(n_sample, n_par)

# Assign parameter and input names
colnames(par_quant) <- par_names

# Create a data frame of parameters and inputs
par_df <- as.data.frame(matrix(nrow = nrow(par_quant), ncol = ncol(par_quant)))

# Assign parameter and input names
colnames(par_df) <- par_names

# Set value for 1% standard deviation
pvar <- 100

## Normal Distribution
# Set parameter sampling to mean and sd given
par_df[,"v"] <- qnorm(par_quant[,"v"], mean = 250, sd = 30)
par_df[,"k_d"] <- qnorm(par_quant[,"k_d"], mean = 0.7, sd = 0.7/pvar)
par_df[,"k_o"] <- qnorm(par_quant[,"k_o"], mean = 0.1, sd = 0.1/pvar)

## Uniform Distribution
# Set height sampling to min and max given
par_df[,"height"] <- qunif(par_quant[,"height"], min = 9.5, max = 10.5)
```

## Atmospheric Conductance Model

Let's now run the atmospheric conductance model for these parameters and
inputs:

```{r}
# Use pmap() to run Catm() for all samples in par_df
ca_outputs <- pmap(par_df, Catm)

# Convert results list into array
output_array <- unlist(ca_outputs)

# Add results array to par_df
par_outputs <- par_df %>%
  mutate(output = output_array)
```

## Plots

Let's plot conductance estimates in a way that accounts for parameter
uncertainty:

```{r warning = FALSE}
# Wrangle data for visualization
par_outputs_long <- par_outputs %>% 
  pivot_longer(cols = !output, # Select all columns except output
               names_to = "parm", # Pivot column names to param column
               values_to = "parmvalue") %>% # Pivot rows to parmvalue column
  mutate(output = as.numeric(output), # Convert to numeric
         parm = as.factor(parm), # Convert to factor
         parmvalue = as.numeric(parmvalue)) # Convert to numeric

# Plot conductance estimates around parameter uncertainty
ggplot(par_outputs_long, aes(y = output)) + 
  geom_boxplot(show.legend = FALSE, aes(col = "#fb5607")) +
  labs(y = "Conductance (mm/s)",
       title = "Conductance estimates with parameter uncertainty") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) 
```

### Parameter Sensitivity

Next, plot conductance estimates against each of your parameters:

```{r}
# Plot conductance estimates against each parameters
ggplot(par_outputs_long, aes(parmvalue, output, col = parm)) + 
  geom_point(show.legend = FALSE) + 
  facet_wrap(~parm, scales = "free", ncol = 2, 
             labeller = labeller(parm = c("height" = "Vegetation height (cm)",
                                          "k_d" = "k_d parameter",
                                          "k_o" = "k_0 parameter",
                                          "v" = "Windspeed (cm/s)"))) +
  labs(y = "Conductance (mm/s)",
       title = "Conductance estimates against parameter uncertainty") +
  theme_classic() +
  theme(axis.title.x = element_blank())
```

## Quantify Sensitivity 3

Let's estimate the Partial Rank Correlation Coefficients:

```{r message = FALSE}
# Apply pcc() for partial rank correlation coefficients 
senresult_rank <- pcc(par_df, par_outputs$output, rank = TRUE)

# View partial rank correlation coefficients results
senresult_rank$PRCC

# Plot partial rank correlation coefficients results
plot(senresult_rank)
```

## Discussion

**What do your results tell you about how aerodynamic conductance? What
does it suggest about what you should focus on if you want to reduce
uncertainty in aerodynamic conductance estimates? Does this tell you
anything about the sensitivity of plant water use to climate change?**

Aerodynamic conductance is most sensitive to the inputs windspeed, $v$,
which is normally distributed, and vegetation height, $height$, which is
uniform distributed. We can improve uncertainty in aerodynamic
conductance estimates by focusing on either input. This is a
consideration for climate change since wind speed will vary with
regional and seasonal variability and plant water use is especially
sensitive.
